The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-18 paper.tex
update

\section{Acknowledgements}
The authors thank Mateusz Ruszkowski and Ellen G. Zweibel for insightful comments.\
We thank Peter Predehl for providing the range of observed X-ray intensity in \Cref{fig__xray_0.8keV_angle_000}.\
A part of the simulations are performed and analyzed using computing resources\
operated by the National Center for High-Performance Computing (NCHC).
HYKY acknowledge support from\
Yushan Scholar Program of the Ministry of Education of Taiwan\
and\
Ministry of Science and Technology of Taiwan (MOST 109-2112-M-007-037-MY3).
HS acknowledges\
funding support from the Jade Mountain Young Scholar Award No. NTU-109V0201,\
sponsored by the Ministry of Education, Taiwan.\
This research is partially supported by the Ministry of Science and\
Technology of Taiwan (MOST) under grants MOST 107-2119-M-002-036-MY3\
and MOST 108-2112-M-002-023-MY3, and the NTU\
Core Consortium project under grants NTU-CC-108L893401 and\
NTU-CC-108L893402.

>>>>

\section{Acknowledgements}
The authors thank Mateusz Ruszkowski and Ellen G. Zweibel for insightful comments.\
We thank Peter Predehl for providing the range of observed X-ray intensity in \Cref{fig__xray_0.8keV_angle_000}.\
A part of the simulations are performed and analyzed using computing resources\
operated by the National Center for High-Performance Computing (NCHC).
HYKY acknowledges support from\
Yushan Scholar Program of the Ministry of Education of Taiwan\
and\
Ministry of Science and Technology of Taiwan (MOST 109-2112-M-007-037-MY3).
HS acknowledges\
funding support from the Jade Mountain Young Scholar Award No. NTU-109V0201,\
sponsored by the Ministry of Education, Taiwan.\
This research is partially supported by the Ministry of Science and\
Technology of Taiwan (MOST) under grants MOST 107-2119-M-002-036-MY3\
and MOST 108-2112-M-002-023-MY3, and the NTU\
Core Consortium project under grants NTU-CC-108L893401 and\
NTU-CC-108L893402.
